A Simple Minibatch Acceptance Test for MCMC

### 2016-06-15 nips_2016.tex
updated a typo

Figure~\ref{fig:gauss_mix_3} (to the left) shows a historgram of ${\rm std}(\Delta')$. Figure~\ref{fig:gauss_mix_3} (to the middle) shows the confidence interval of our estimated ${\rm std}(\Delta')$ at each iteration \footnote{In order to show the confidence interval clearly, we use moving smooth to smooth the confidence interval, and plot each value by interval of 50 iterations}. The blue line represents the standard deviation comes from the complete data, which can be treated as the ``true'' ${\rm std}(\Delta')$, the green line represents our estimation of ${\rm std}(\Delta')$ from the minibatch, and the two red dash lines represent the confidence interval of ${\rm std}(\Delta')$ by adding / subtracking one ${\rm std(std(}\Delta'))$. This figure indicates that our estimation of ${\rm std}(\Delta')$ from one minibatch data is accurate. Figure~\ref{fig:gauss_mix_3} (to the right) shows the value of $\rho/\sigma^3$ at each iteration. Recall Theorem~\ref{thm:efficiency}, the number of data instance required is $\frac{4 \ell^2 C^2 \rho^2 }{\sigma^6 \varepsilon^2}$. This figure reveals that $\rho/\sigma^3$ is rougly a constant, which means the data required for each iteration is a constant value has nothing to do with the $N$.

>>>>

Figure~\ref{fig:gauss_mix_3} (to the left) shows a historgram of ${\rm std}(\Delta')$. Figure~\ref{fig:gauss_mix_3} (to the middle) shows the confidence interval of our estimated ${\rm std}(\Delta')$ at each iteration \footnote{In order to show the confidence interval clearly, we use moving smooth to smooth the confidence interval, and plot each value by interval of 50 iterations}. The blue line represents the standard deviation comes from the complete data, which can be treated as the ``true'' ${\rm std}(\Delta')$, the green line represents our estimation of ${\rm std}(\Delta')$ from the minibatch, and the two red dash lines represent the confidence interval of ${\rm std}(\Delta')$ by adding / subtracking one ${\rm std(std(}\Delta'))$. This figure indicates that our estimation of ${\rm std}(\Delta')$ from one minibatch data is accurate. Figure~\ref{fig:gauss_mix_3} (to the right) shows the value of $\rho/\sigma^3$ at each iteration. Recall Theorem~\ref{thm:efficiency}, the number of data instance required is $\frac{4 \ell^2 C^2 \rho^2 }{\sigma^6 \varepsilon^2}$. This figure reveals that $\rho/\sigma^3$ is rougly a constant, which means the data required for each iteration is a constant value which has nothing to do with the $N$.
